\bf Visual Inference for Significance and Goodness-of-Fit Testing for a Social Network Model

### 2017-10-30 ASApaper/paper-child.Rnw
add 1/6 line to plots

<<predictglmm, fig.height=6, fig.cap='Predictions from our generalized linear mixed effects model given in Equation~\ref{eq:glmm}. The lines show the expected probability of detecting the alternative data in a lineup of size 6 for new observers of new lineups is plotted on the $y$-axis, and the size of the parameter of interest is on the $x$-axis. The proportions detected by our Turk participants for each lineup group are shown by the points. The lineup marked as ``outlier" was removed from modeling. The ``recip" panel is also presented in Figure~\\ref{fig:recipzoom} in more detail.'>>=
newdata <- read_csv("data/newdata_pred_glmm.csv")
newdata$param <- newdata$test_param
newdata$param <- as.factor(newdata$test_param)
levels(newdata$param) <- c("beta[1]", "beta[3]", "beta[4]", "beta[2]", "beta[6]", "beta[5]")
newdata$param <-as.character(newdata$param)
plotdata <- turk22 %>% mutate(type2 = ifelse(sign == 0, sign(initialEst), sign),
                       type2 = ifelse(type == "one", type2, -1)) %>% 
  group_by(pic_id, size, test_param, sign, type2,alt_model) %>% summarize(
    datapick = mean(datapick)
)
plotdata$param <- plotdata$test_param
plotdata$param <- as.factor(plotdata$param)
levels(plotdata$param) <- c("beta[1]", "beta[3]", "beta[4]", "beta[2]", "beta[6]", "beta[5]")
plotdata$param <- as.character(plotdata$param)
labdat <- data_frame(test_param = "jttp", param = "beta[3]", type2 = -1, x = -5, y = .9, label = "outlier")

ggplot() + 
  geom_line(data = newdata, aes(x = size, y = predictfinal, color = as.factor(type2))) + 
  geom_point(data = plotdata, aes(x = size, y = datapick, color = as.factor(type2))) + 
  #geom_text(data = plotdata, aes(x = size, y = datapick, color = as.factor(type2), label = pic_id)) +
  geom_text(data = labdat, aes(x = x, y=y, label = label, color = as.factor(type2)),
            show.legend = F) +

  scale_color_brewer(palette = "Dark2", name = "Lineup Type") + 
  facet_wrap(~param, scales = 'free_x', labeller = label_parsed) + 
  labs(x = "Parameter value", y = "Expected probability of detection in a lineup of size 6") + 
  ThemeNoNet + 
  theme(legend.position = 'bottom')

@@

<<recipzoom, fig.height=2.5, fig.cap='The top middle panel of Figure~\\ref{fig:predictglmm} expanded to show greater detail. For this parameter, as its value approaches zero, the probability of identifying the alternate data model decreases, then increases, which is noticeably different from the pattern exhibited by the others.'>>=
ggplot() + 
  geom_line(data = newdata %>% filter(test_param == "recip"), aes(x = size, y = predictfinal, color = as.factor(type2))) + 
  geom_point(data = plotdata %>% filter(test_param == "recip"), aes(x = size, y = datapick, color = as.factor(type2))) + 
  scale_color_brewer(palette = "Dark2", name = "Lineup Type") + 
  facet_wrap(~type2, scales = 'free_x') + 
  labs(x = "Parameter value (recip)", y = "Expected probability of detection\nin a lineup of size 6") + 
  ThemeNoNet + 
  theme(legend.position = 'bottom')
@

>>>>

<<predictglmm, fig.height=6, fig.cap='Predictions from our generalized linear mixed effects model given in Equation~\ref{eq:glmm}. The lines show the expected probability of detecting the alternative data in a lineup of size 6 for new observers of new lineups is plotted on the $y$-axis, and the size of the parameter of interest is on the $x$-axis. The proportions detected by our Turk participants for each lineup group are shown by the points, with the probability of picking out the data plot at random shown by a horizontal line at 1/6. The lineup marked as ``outlier" was removed from modeling. The panel for the reciprocity parameter, $\\beta_2$ is also presented in Figure~\\ref{fig:recipzoom} in more detail.'>>=
newdata <- read_csv("data/newdata_pred_glmm.csv")
newdata$param <- newdata$test_param
newdata$param <- as.factor(newdata$test_param)
levels(newdata$param) <- c("beta[1]", "beta[3]", "beta[4]", "beta[2]", "beta[6]", "beta[5]")
newdata$param <-as.character(newdata$param)
plotdata <- turk22 %>% mutate(type2 = ifelse(sign == 0, sign(initialEst), sign),
                       type2 = ifelse(type == "one", type2, -1)) %>% 
  group_by(pic_id, size, test_param, sign, type2,alt_model) %>% summarize(
    datapick = mean(datapick)
)
plotdata$param <- plotdata$test_param
plotdata$param <- as.factor(plotdata$param)
levels(plotdata$param) <- c("beta[1]", "beta[3]", "beta[4]", "beta[2]", "beta[6]", "beta[5]")
plotdata$param <- as.character(plotdata$param)
labdat <- data_frame(test_param = "jttp", param = "beta[3]", type2 = -1, x = -5, y = .9, label = "outlier")

ggplot() + 
  geom_line(data = newdata, aes(x = size, y = predictfinal, color = as.factor(type2))) + 
  geom_point(data = plotdata, aes(x = size, y = datapick, color = as.factor(type2))) + 
  #geom_text(data = plotdata, aes(x = size, y = datapick, color = as.factor(type2), label = pic_id)) +
  geom_text(data = labdat, aes(x = x, y=y, label = label, color = as.factor(type2)),
            show.legend = F) + 
  geom_hline(yintercept = 1/6, linetype='dashed') +
  scale_color_brewer(palette = "Dark2", name = "Lineup Type") + 
  facet_wrap(~param, scales = 'free_x', labeller = label_parsed) + 
  labs(x = "Parameter value", y = "Expected probability of detection in a lineup of size 6") + 
  ThemeNoNet + 
  theme(legend.position = 'bottom')

@@

<<recipzoom, fig.height=2.5, fig.cap='The top middle panel of Figure~\\ref{fig:predictglmm} expanded to show greater detail. For this parameter, as its value approaches zero, the probability of identifying the alternate data model decreases, then increases, which is noticeably different from the pattern exhibited by the others. Again, a horizontal line is drawn at 1/6, the chance of selecting the data plot at random.'>>=
ggplot() + 
  geom_line(data = newdata %>% filter(test_param == "recip"), aes(x = size, y = predictfinal, color = as.factor(type2))) + 
  geom_point(data = plotdata %>% filter(test_param == "recip"), aes(x = size, y = datapick, color = as.factor(type2))) + 
  scale_color_brewer(palette = "Dark2", name = "Lineup Type") + 
  geom_hline(yintercept = 1/6, linetype='dashed') + 
  facet_wrap(~type2, scales = 'free_x') + 
  labs(x = "Parameter value (recip)", y = "Expected probability of detection\nin a lineup of size 6") + 
  ThemeNoNet + 
  theme(legend.position = 'bottom')
@
